Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-04 paper/ms.tex
Add caveat about solar radius
Fix typo

The top row of Figure~\ref{Fig:many_orbit_wrong_ref} shows the error in each
action assuming an offset in the $z$ component (i.e. the Galactic midplane).
In the {\em bottom row} we also consider offsets in the $x$ component (i.e.
the Solar radius). The {\em left}, {\em middle}, and {\em right} columns show
the relative error in $J_z$, $L_z$, and $J_r$, respectively. We compute the
relative error as the  95\uth minus 5\uth percentile of the measured action
($\Delta J_i$) over the course of the first $\Gyr$ of the incorrectly observed
orbit divided by the true action value as a percentage.

@@

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission.

>>>>

The top row of Figure~\ref{fig:many_orbit_wrong_ref} shows the error in each
action assuming an offset in the $z$ component (i.e. the Galactic midplane).
In the {\em bottom row} we also consider offsets in the $x$ component (i.e.
the Solar radius). The {\em left}, {\em middle}, and {\em right} columns show
the relative error in $J_z$, $L_z$, and $J_r$, respectively. We compute the
relative error as the  95\uth minus 5\uth percentile of the measured action
($\Delta J_i$) over the course of the first $\Gyr$ of the incorrectly observed
orbit divided by the true action value as a percentage.

@@

\section{Discussion} \label{sec:discussion}
We have shown that, in simulation, the ``local midplane'' can have strong
azimuthal dependence. The implications of this finding are not clear, but
clearly demonstrate that assuming our local midplane is the same as the global
midplane is insufficient for extracting the most dynamical information from
the {\em Gaia} mission. From now on, we set aside the discussion of
inaccuracies in the Solar radius. While all that we state about the midplane
applies to the Solar radius as well, it is not clear the best way to determine
the dynamical center of the galaxy in the FIRE simulations.
